\LARGE \bf Approximately Orchestrated Road Traffic Automata\\ a General Traffic Simulation Framework

### 2012-03-07 papers/itsc_2012/draft2.tex
wrote a conclusion

\section{CONCLUSIONS}
\label{sec:conclusion}

Write me. big future ideas:

\commentp{Proposed improvements to OSM data would be great for a
  discussion or conclusion section at the end of the paper.}
proposals to change OSM to fix these issues
  projecting lines sucks... but all it really does is clutter UI
  filtering out invalid ways in pass 1 is really not a clear process
  number of lanes and speed limits... road types are wacky and wrong
  turns are brittle.. detecting right-turn only lane is rare. shared center lane?
    not part of our model, or OSM's.
  removing sccs is not ideal

contraflow

microtolling

dynamic replanning

autonomous intersections

@@

% Notes.

%possible background/links

%http://www.caliper.com/transmodeler/default.htm
%http://ieeexplore.ieee.org/stamp/stamp.jsp?tp=&arnumber=6082793
%https://www.google.com/search?sourceid=chrome&ie=UTF-8&q=Agent-Based+Traffic+Simulation+and+Traffic+Signal+Timing+Optimization+with+GPU

>>>>

\section{CONCLUSION}
\label{sec:conclusion}

This paper has presented AORTA, a new city-scale traffic simulation framework
that focuses on ease-of-use and policy configurability. In conjunction with Open
Street Maps, AORTA allows researchers to repeat an experiment in any number of
places with minimal effort. Future work will exploit the flexible infrastructure
of interactions between agent behaviors and intersections by exploring dynamic
replanning and adaptable signal timings. On top of these structures,
applications could experiment with contra-flow \commentd{cite these all} and
micro-tolling. There will also be an effort to improve AORTA as a framework by
including a lane-changing model and preventing gridlock.

AORTA's map construction process, although flexible, is fraught with heuristics,
motivating proposed changes to OSM. Road type annotations imprecisely estimate
the number of lanes and typical speed limits, resulting in incorrect graphs.
Guessing the turns at each intersection makes common road features like right
turn-only lanes and shared center left turn lanes hard to detect. There are many
circumstances where AORTA simulates one intersection as several in close
proximity because roads do not geometrically line up, but semantically they do.
If OSM could encode this, the performance of intersection policies such as
traffic signals would vastly improve in those regions.

\commentd{Er, so how do I finally end this?}

@@
